Holomorphic field theories and higher algebra

### 2022-10-03 draft.tex
added some improvements to final subsections

In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories flow to the same superconformal fixed point in the infrared limit. 
This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window''
(note that it is preserved under swapping $N \leftrightarrow F-N$).
Here we will explore how it appears from the point of view of holomorphic QCD.

@@

\subsection{A second pass at holomorphic Seiberg duality, and its relations to Hori-Tong duality}

@@

On the other hand, there is an open locus where the moduli stacks are equivalent:
the semi-stable points of $[V/G]$ \owen{fix description, as it's possibly just the stable locus}.
This locus determines the space $V\Sslash G$ and hence we have the isomorphism desired.
Let us try to unravel what this equivalence means for the field theories, both classical and quantum.

Consider any semistable point $x$ in $[V/G]s$.
We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x (V//G)$ \owen{Elaborate}. 
Hence the isomorphism of moduli spaces assures us there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$
because there is an explicit identification of the tangent space to the corresponding point in the moduli space of the dual theory.
Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
Hence on the semistable locus of $[V/G]$, we can guarantee an equivalence of quantizations.

This identification breaks down on the unstable locus, raising the following question.

{\bf Question:}
At the quantum level, what happens on the unstable locus?

In a related vein, we want to know what correspondence of quantum factorization algebras we expect from Seiberg duality. 
The mismatch for the moduli stack of classical vacua must be fixed somehow.

\owen{Other things: affinization as polydiscs algebras, comparison with mirror symmetry (note A-model involves instanton corrections)}

Conjecture: There is an equivalence of affinizations of the quantum moduli stacks for Seiberg dual theories.

This process probably looks away from the unstable locus in the same way that the classical part does.

>>>>

In the original version of Seiberg duality, there are certain values of $F$ and $N$ where the dual theories flow to the same superconformal fixed point in the infrared limit. 
This range of values $F/3 < N < 2F/3$ is known as the ``superconformal window.''
(Note that it is preserved under swapping $N \leftrightarrow F-N$.)
Here we will explore how it appears from the point of view of holomorphic QCD.

@@

\owen{Should we check that the quantum magnetic theory also has a divergence-free symmetry?}

\subsection{A relation to Hori-Tong duality}

A beautiful maneuver of physics is compactification, where one takes a field theory $\cT$ in $n$ dimensions and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
We have already worked with a factorization algebra version of these maneuvers: 
pushing forward along the map $\rho: \C^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
We now apply this result in the context of holomorphic QCD and see what Seiberg duality would mean.

\begin{lmm}
For a holomorphic QCD theory, this compactification is a Landau-Ginzburg B-model for \owen{finish! would it be easier just to spell out what happens to matter, gauge, and the QCD?}
\end{lmm}

Holomorphic Seiberg duality then predicts an equivalence of two-dimensional topological field theories,
or at least of $E_2$-algebras.

\begin{conj}
\owen{Unpack in some detail.}
\end{conj}

This conjecture is essentially due to Hori and Tong. \owen{Add some history, cite some references.}

\subsection{A second pass at holomorphic Seiberg duality}

In our attempts above to explore (and test) Eager's conjecture, we developed insights and highlighted issues that help to refine it.

On the other hand, there is an open locus where the moduli stacks are equivalent:
the semi-stable points of the moduli stacks $\cM_{\rm vac}$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
This locus determines the space $V\Sslash G$ and hence we have the isomorphism desired.
Let us try to unravel what this equivalence means for the field theories, both classical and quantum.

Consider any semistable point $x$.
We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x \cM_{\rm vac}$ \owen{Elaborate: more accurately, it's into the formal neighborhood}. 
Hence the isomorphism of moduli spaces assures us there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$
because there is an explicit identification of the tangent space to the corresponding point in the moduli space of the dual theory.
Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
Hence on the semistable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.

This identification breaks down on the unstable locus, raising the following question:
\begin{quote}
At the quantum level, what happens on the unstable locus? 
\end{quote}
Each unstable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
and hence its quantization is more involved that at a semistable point and depends nontrivially the gauge group.

In a related vein, we want to know what correspondence of quantum factorization algebras we expect from Seiberg duality. 
The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.

\owen{Other things: affinization as polydiscs algebras}

\begin{conj}
There is an equivalence of affinizations of the quantum moduli stacks for Seiberg dual theories.
That is, the quantum moduli spaces are isomorphic.
\end{conj}

This process probably ``looks away'' from the unstable locus in much the way that it does at the classical level,
which provided our identification of moduli spaces of classical vacua.

*********** Discuss enhanced spacetime symmetries ****************

@@
